### 2016-06-29 sec5_spm.tex
An almost complete version
Near Done
With Prof Tan's Comments
With prof's comment

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\textwidth]{spm.eps}
\caption{Star partition and ApRiori Enumerator (SPARE). (a) Aggregate graph from Figure 1. (b) Five stars are generated, star IDs are circled, the vertexes and inverted lists are in the connected tables.
(c) Apriori Enumerator with various pruning techniques.}
\label{fig:star_partition}
\end{figure*}

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned replicate partitioning is based on the temporal dimension which suffers from two drawbacks. First, the replication relies on $\eta$ which could be large. Second, the same valid pattern may be discovered from different partitions which results in redundant works.
To resolve the limitations caused by the replicate partitioning, 
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMP patterns. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

\subsection{Star Partitioning}
Let $G_t$ be a graph for snapshot $S_t$, in which each node 
is a moving object and two objects are connected if they appear 
in the same cluster. It is obvious that $G_t$ consists of a set of small cliques. 
Based on $G_t$, we define an aggregated graph $G_A$ to summarize the 
cluster relationship among all the snapshots. In $G_A$, two objects
form an edge if they are connected in any $G_t$s. Furthermore, 
we attach an inverted list for each edge, 
storing the associated timestamps in which the two objects are connected. 
An example of $G_A$, built on the trajectory database in Figure~\ref{fig:related_work}, 
is shown in Figure~\ref{fig:star_partition} (a). 
As long as two objects are clustered in any timestamps, they are connected in $G_A$. 
The object pair $\langle o_1,o_2 \rangle$ appears in two clusters at timestamps 
$2$ and $3$ and is thus associated with an inverted list $(2,3)$.

@@

With the global ordering, we can guarantee that each edge is contained in a unique star partition. Given the aggregated graph $G_A$  in Figure~\ref{fig:star_partition} (a), we enumerate all the possible directed stars in Figure~\ref{fig:star_partition} (b). These stars are emitted from mappers to different reducers. The key is the star ID and the value is the neighbors in the star as well as the associated inverted lists. 
The reducer will then call the Apriori-based algorithm to enumerate all the valid GCMP patterns.

Before we introduce the Apriori enumerator, we are interested to 
examine the issue of global ordering on the moving objects.
This is because assigning different IDs to the objects will result in 
different star partitioning results, which will eventually affect the workload 
balance among the map-reduce jobs. The job incurring performance bottleneck is often known as \emph{straggler}~\cite{kwon2012skewtune,xin2013shark,coppa2015data}. In the context of star partitioning, a straggler refers to the job assigned with the maximum star partition. We use $\Gamma$ to denote the size of a partition and $\Gamma$ is set to the number of edges in a directed star\footnote{A star is essentially a tree structure and the number of nodes equals the number of edges minus one.}. It is straightforward that a star partitioning with small $\Gamma$ is preferred. For example, Figure~\ref{fig:star-alt} gives two star partitioning results under 
different vertex ordering on the same graph. The top one has $\Gamma = 5$ while the bottom one has $\Gamma = 3$. Obviously, the bottom one with smaller $\Gamma$ is much more balanced.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{star-alt.eps}
\caption{Examples of star partitioning with different vertex ordering.}
\label{fig:star-alt}
\end{figure}

@@

\begin{theorem}
\label{THM:SPM_LB}
Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be value derived from a random vertex ordering. With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}
\begin{proof}
In Appendix~\ref{apx:thm2proof}.
\end{proof}
If $G_A$ is a dense graph, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
\begin{theorem}
\label{THM:SPM_LB_INC}
Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
\end{theorem}
\begin{proof}
In Appendix~\ref{apx:thm2proof}.
\end{proof}
Hence, we can simply use object id to determine the vertex ordering in our implementation.

@@

\subsubsection{Monotonicity}
To ensure the monotonicity, we first introduce a procedure named \textit{star simplification}, to reduce the number of edges as well as unnecessary timestamps in the inverted lists. For instance, if the size of the inverted list for an edge $e$ is smaller than $K$, then the edge can be safely removed because the number of timestamps in which its supersets are clustered must also be smaller than $K$. To generalize the idea, we propose three concepts named \textit{maximal $G$-connected subsequence}, \emph{decomposable sequence} and \emph{sequence simplification}.

@@

To prove (2), we assume $\cup_i T_i$ does not cover all the timestamps in $T$. Then, we can find a subsequence $T'=T[x:x+t]$ such that $T[x-1]\in T_a$ $(1\leq a\leq m)$, $T[x+t+1]\in T_b$ $(1\leq b\leq m)$ and all the timestamps in $T'$ is not included in any $T_i$. Let $g'=\min\{T[x]-T[x-1], T[x+t+1]-T[x+t]\}$. If $g'\leq G$, then it is easy to infer that $T_a$ or $T_b$ is not a maximal $G$-connected subsequence because we can combine it with $T[x]$ or $T[x+t]$  to a form superset which is also $G$-connected. If $g'>G$, $T'$ itself is a maximal $G$-connected subsequence which is missed in $\cup T_i$. Both cases lead to contradiction.
\end{proof}

@@

With Lemma~\ref{lemma:decom-sim}, we are ready to define the \emph{monotonicity} based on the simplified
sequences to facilitate the pruning in the Apriori algorithm.

@@

\begin{proof}
We prove by contradiction. Suppose there exists a valid pattern $P_2$ such that $P_2.O \supseteq P.O$. It is obvious that $P_2.T \subseteq P.T$. Based on the Definition 2, the following conditions hold: (1) $P_2.T$ is $G$-connected. (2) $|P_2.T| \geq K$ and (3) $P_2.T$ is $L$-consecutive. Note that the entire $P_2.T$ is $G$-connected. Thus, $P_2.T$ itself is the only maximal $G$-connected subsequence. Based on conditions (1),(2),(3) and Definition 6, $P_2.T$ is decomposable. Then, based on Lemma~\ref{lemma:decom-sim}, we know $\mathtt{sim}(T)\neq \emptyset$ because $P_2.T \subseteq P.T$ and $P_2.T$ is decomposable. This leads to a contradiction with $\mathtt{sim}(P.T)=\emptyset$.
\end{proof}

@@

\begin{algorithm}[h]
\caption{Apriori Enumerator}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$C \leftarrow \emptyset$}
\ForAll{edges $c=\langle o_i\cup o_j, T_{o_i}\cap T_{o_j}\rangle$ in $Sr_s$} \label{code:init-start}
\If {$\mathtt{sim}(T_{o_i}\cap T_{o_j})\neq \emptyset$}
\State {$C\leftarrow C\cup \{c\}$} \label{code:simp1}
\EndIf 
\EndFor\label{code:init-end}
\State $\mathrm{level} \gets 2$ \label{code:level}
\While{$C\neq \emptyset$} \label{code:level-start}
	\ForAll{$c_1 \in C$}
		\ForAll{$c_2 \in C$ and $|c_2.O \cup c_2.O| = \mathrm{level}$}\label{code:join-start}	
			\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}			
			\If{ $\mathtt{sim}(c'.T)\neq \emptyset$} \label{code:simp2}
					\State {$C'\leftarrow C'\cup \{c'\}$}
			\EndIf			
		\EndFor\label{code:join-end}
		\If {no $c'$ is added to $C'$} \label{code:output1-start}
			\If{$c_1$ is a valid pattern}
				\State output $c_1$
			\EndIf
		\EndIf \label{code:output1-end}
	\EndFor
	\State $O_u \gets $ union of $c.O$ in $C$	\label{code:fc-checking-start}
	\State $T_u \gets $ intersection of $c.T$ in $C$	
	\If {$\langle O_u, T_u\rangle$ is a valid pattern}
		\State{output $\langle O_u, T_u\rangle$} \label{code:fc-checking}
		\State break;
	\EndIf \label{code:fc-checking-end}
	\State {$C\leftarrow C';C'\leftarrow \emptyset; \mathrm{level} \gets \mathrm{level}+1$}	
\EndWhile\label{code:level-ends}
\State output $C$ \label{code:output2-end}
\end{algorithmic}
\end{algorithm}

@@

\subsection{Put It Together}
We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, for ease of presentation, we used an aggregated graph $G_A$ to capture the clustering relationship. However, in the implementation of the map phase, there is no need to create $G_A$ in advance. Instead, we simply need to emit the edges within a star to the same reducer. Before sending stars to reducers, we use a simple best-fit strategy to calculate the star allocation. In best-fit strategy, the most costly unallocated star is assigned to the most empty reducers, where we use the edges in the star as a cost estimation.
 Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a candidate pattern $\langle o,i: e(o,i) \rangle$ is created. Then it enumerates all the valid patterns from the candidate patterns. The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.

\begin{algorithm}
\small
\caption{Star Partition and ApRiori Enumerator}
\label{algo:spm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map phase---}
\label{code:spm-map-start}
\ForAll{$C \in S_t$}
	\ForAll {$o_1 \in C,  o_2 \in C, o_1 < o_2$}
	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet~\label{code:spm-edge-direct}
	\EndFor
\EndFor
\label{code:spm-map-end}

\State {---Partition and Shuffle phase---}
\label{code:spm-shuffle-start}
\ForAll{$\langle o_1, o_2, \{t\}\rangle$ triplets} 
	\State group-by $o_1$, emit $\langle o_1, Sr_{o_1} \rangle$ 
\EndFor
\label{code:spm-shuffle-end}

\State {---Reduce phase---}
\label{code:spm-reduce-start}
\ForAll{$\langle o, Sr_{o} \rangle$}
\State AprioriEnumerator($Sr_o$)
\EndFor
\label{code:spm-reduce-end}

@@

Compared with TPMP, the SPARE framework does not rely on snapshot replication to guarantee correctness. In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
\begin{theorem}[Pattern Uniqueness]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \neq p_j.O$.
\end{theorem}
\begin{proof}
We prove by contradiction. Suppose there exist $p_i \in P_i$ and $p_j \in P_j$ with the same object set. Note that the center vertex of the star is associated with the minimum id. Let $o_i$ and $o_j$ be the center vertices of the two partitions and we have $o_i=o_j$. However, $P_i$ and $P_j$ are different stars, meaning their center vertices are different (i.e., $o_i\neq o_j$), leading to a contradiction. 
\end{proof}

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we prove the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
See Appendix~\ref{apx:spm_correct}.
\end{proof}

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\textwidth]{spm.eps}
\caption{Star partition and ApRiori Enumerator (SPARE). (a) Aggregated graph from Figure 1. (b) Five stars are generated, star IDs are circled, the vertexes and inverted lists are in the connected tables.
(c) Apriori Enumerator with various pruning techniques.}
\label{fig:star_partition}
\end{figure*}

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned TRPM scheme replicates partitions based on the temporal dimension which suffers from two drawbacks. First, the replication factor is $\eta$ which can be large. Second, the same valid pattern may be discovered from different partitions which results in redundant works.
To resolve these limitations,
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second stage of map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMP patterns. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

\subsection{Star Partitioning}
Let $G_t$ be a graph for snapshot $S_t$, in which each node 
is a moving object and two objects are connected if they appear 
in the same cluster. It is obvious that $G_t$ consists of a set of small cliques. 
Based on $G_t$, we define an aggregated graph $G_A$ to summarize the 
cluster relationship among all the snapshots. In $G_A$, two objects
form an edge if they are connected in any $G_t$s. Furthermore, 
we attach an inverted list for each edge, 
storing the associated timestamps in which the two objects are connected. 
An example of $G_A$, built on the trajectory database in Figure~\ref{fig:related_work}, 
is shown in Figure~\ref{fig:star_partition}(a). 
As long as two objects are clustered in any timestamps, they are connected in $G_A$. 
The object pair $\langle o_1,o_2 \rangle$ appears in two clusters at timestamps 
$2$ and $3$ and is thus associated with an inverted list $(2,3)$.

@@

With the global ordering, we can guarantee that each edge is contained in a unique star partition. Given the aggregated graph $G_A$  in Figure~\ref{fig:star_partition}(a), we enumerate all the possible directed stars in Figure~\ref{fig:star_partition}(b). These stars are emitted from mappers to different reducers. The key is the star ID and the value is the neighbors in the star as well as the associated inverted lists. 
The reducer will then call the Apriori-based algorithm to enumerate all the valid GCMP patterns.

Before we introduce the Apriori enumerator, we are interested to 
examine the issue of global ordering on the moving objects.
This is because assigning different IDs to the objects will result in 
different star partitioning results, which will eventually affect the workload 
balance among the map-reduce jobs. The job with the performance bottleneck is often known as a  \emph{straggler}~\cite{kwon2012skewtune,coppa2015data}. In the context of star partitioning, a straggler refers to the job assigned with the maximum star partition. We use $\Gamma$ to denote the size of a partition and $\Gamma$ is set to the number of edges in a directed star\footnote{A star is essentially a tree structure and the number of nodes equals the number of edges minus one.}. Clearly, a star partitioning with small $\Gamma$ is preferred. For example, Figure~\ref{fig:star-alt} gives two star partitioning results under 
different vertex ordering on the same graph. The top one has $\Gamma = 5$ while the bottom one has $\Gamma = 3$. Obviously, the bottom one with smaller $\Gamma$ is much more balanced.

\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{star-alt.eps}
\caption{Examples of star partitioning with different vertex ordering.}
\label{fig:star-alt}
\end{figure}

@@

\begin{theorem}
\label{THM:SPM_LB}
Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be the value derived from a random vertex ordering. With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}
\begin{proof}
In Appendix~\ref{apx:thm2proof}.
\end{proof}
If $G_A$ is a dense graph, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
\begin{theorem}
\label{THM:SPM_LB_INC}
Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
\end{theorem}
\begin{proof}
In Appendix~\ref{apx:thm2proof}.
\end{proof}
Hence, we can simply use object id to determine the vertex ordering in our implementation.

@@

\subsubsection{Monotonicity}
To ensure monotonicity, we first introduce a procedure named \textit{star simplification}, to reduce the number of edges as well as unnecessary timestamps in the inverted lists. For instance, if the size of the inverted list for an edge $e$ is smaller than $K$, then the edge can be safely removed because the number of timestamps in which its supersets are clustered must also be smaller than $K$. To generalize the idea, we propose three concepts named \textit{maximal $G$-connected subsequence}, \emph{decomposable sequence} and \emph{sequence simplification}.

@@

To prove (2), we assume $\cup_i T_i$ does not cover all the timestamps in $T$. Then, we can find a subsequence $T'=T[x:x+t]$ such that $T[x-1]\in T_a$ $(1\leq a\leq m)$, $T[x+t+1]\in T_b$ $(1\leq b\leq m)$ and all the timestamps in $T'$ is not included in any $T_i$. Let $g'=\min\{T[x]-T[x-1], T[x+t+1]-T[x+t]\}$. If $g'\leq G$, then it is easy to infer that $T_a$ or $T_b$ is not a maximal $G$-connected subsequence because we can combine it with $T[x]$ or $T[x+t]$  to a form superset which is also $G$-connected. If $g'>G$, $T'$ itself is a maximal $G$-connected subsequence which is missed in $\cup T_i$. Both cases lead to a contradiction.
\end{proof}

@@

With Lemma~\ref{lemma:decom-sim}, we are ready to define the \emph{monotonicity} concept based on the simplified
sequences to facilitate the pruning in the Apriori algorithm.

@@

\begin{proof}
We prove by contradiction. Suppose there exists a valid pattern $P_2$ such that $P_2.O \supseteq P.O$. It is obvious that $P_2.T \subseteq P.T$. Based on Definition 2, the following conditions hold: (1) $P_2.T$ is $G$-connected. (2) $|P_2.T| \geq K$ and (3) $P_2.T$ is $L$-consecutive. Note that the entire $P_2.T$ is $G$-connected. Thus, $P_2.T$ itself is the only maximal $G$-connected subsequence. Based on conditions (1),(2),(3) and Definition 6, $P_2.T$ is decomposable. Then, based on Lemma~\ref{lemma:decom-sim}, we know $\mathtt{sim}(T)\neq \emptyset$ because $P_2.T \subseteq P.T$ and $P_2.T$ is decomposable. This leads to a contradiction with $\mathtt{sim}(P.T)=\emptyset$.
\end{proof}

@@

\begin{algorithm}[h]
\caption{Apriori Enumerator}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$C \leftarrow \emptyset$}
\ForAll{edges $c=\langle o_i\cup o_j, T_{o_i}\cap T_{o_j}\rangle$ in $Sr_s$} \label{code:init-start}
\If {$\mathtt{sim}(T_{o_i}\cap T_{o_j})\neq \emptyset$}
\State {$C\leftarrow C\cup \{c\}$} \label{code:simp1}
\EndIf 
\EndFor\label{code:init-end}
\State $\mathrm{level} \gets 2$ \label{code:level}
\While{$C\neq \emptyset$} \label{code:level-start}
	\ForAll{$c_1 \in C$}
		\ForAll{$c_2 \in C$ and $|c_2.O \cup c_2.O| = \mathrm{level}$}\label{code:join-start}	
			\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}			
			\If{ $\mathtt{sim}(c'.T)\neq \emptyset$} \label{code:simp2}
					\State {$C'\leftarrow C'\cup \{c'\}$}
			\EndIf			
		\EndFor\label{code:join-end}
		\If {no $c'$ is added to $C'$} \label{code:output1-start}
			\If{$c_1$ is a valid pattern}
				\State output $c_1$
			\EndIf
		\EndIf \label{code:output1-end}
	\EndFor
	\State $O_u \gets $ union of $c.O$ in $C$	\label{code:fc-checking-start}
	\State $T_u \gets $ intersection of $c.T$ in $C$	
	\If {$\langle O_u, T_u\rangle$ is a valid pattern}
		\State{output $\langle O_u, T_u\rangle$, \textbf{break}} \label{code:fc-checking}
	\EndIf \label{code:fc-checking-end}
	\State {$C\leftarrow C';C'\leftarrow \emptyset; \mathrm{level} \gets \mathrm{level}+1$}	
\EndWhile\label{code:level-ends}
\State output $C$ \label{code:output2-end}
\end{algorithmic}
\end{algorithm}

@@

\subsection{Put It Together}
We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, for ease of presentation, we used an aggregated graph $G_A$ to capture the clustering relationship. However, in the implementation of the map phase, there is no need to create $G_A$ in advance. Instead, we simply need to emit the edges within a star to the same reducer. Before sending stars to reducers, we use a simple best-fit strategy to calculate the star allocation. Under the best-fit strategy, the most costly unallocated star is assigned to the most lightly loaded reducers, where we use the edges in the star as a cost estimation.
 Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a candidate pattern $\langle o,i: e(o,i) \rangle$ is created. Then it enumerates all the valid patterns from the candidate patterns. The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.

\begin{algorithm}
\small
\caption{Star Partition and ApRiori Enumerator}
\label{algo:spm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {\textit{---Map phase---}}
\label{code:spm-map-start}
\ForAll{$C \in S_t$}
	\ForAll {$o_1 \in C,  o_2 \in C, o_1 < o_2$}
	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet~\label{code:spm-edge-direct}
	\EndFor
\EndFor
\label{code:spm-map-end}

\State {\textit{---Partition and Shuffle phase---}}
\label{code:spm-shuffle-start}
\ForAll{$\langle o_1, o_2, \{t\}\rangle$ triplets} 
	\State group-by $o_1$, emit $\langle o_1, Sr_{o_1} \rangle$ 
\EndFor
\label{code:spm-shuffle-end}

\State {\textit{---Reduce phase---}}
\label{code:spm-reduce-start}
\ForAll{$\langle o, Sr_{o} \rangle$}
\State AprioriEnumerator($Sr_o$)
\EndFor
\label{code:spm-reduce-end}

@@

Compared with TRPM, the SPARE framework does not rely on snapshot replication to guarantee correctness. In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
\begin{theorem}[Pattern Uniqueness]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \neq p_j.O$.
\end{theorem}
\begin{proof}
We prove by contradiction. Suppose there exist $p_i \in P_i$ and $p_j \in P_j$ with the same object set. Note that the center vertex of the star is associated with the minimum id. Let $o_i$ and $o_j$ be the center vertices of the two partitions and we have $o_i=o_j$. However, $P_i$ and $P_j$ are different stars, meaning their center vertices are different (i.e., $o_i\neq o_j$), leading to a contradiction. 
\end{proof}

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
See Appendix~\ref{apx:spm_correct}.
\end{proof}
